%% start of file `template_en.tex'.
%% Copyright 2006-1008 Xavier Danaux (xdanaux@gmail.com).
% 
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[10pt,a4paper]{moderncv}
\moderncvtheme[blue]{classic}                

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{graphicx}

\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[scale=0.9]{geometry}
\setlength
\AtBeginDocument{\recomputelengths}

\firstname{François-Xavier}
\familyname{\\Matthews}
\title{Datamining student}
\address{21, avenue de la mare aux daims, A206}{76800 Saint-Etienne-Du-Rouvray, France}  
\extrainfo{
  French\\
  Driving license
}

\newcommand{\matlab}{\textbf{Matlab}}
\newcommand{\java}{\textbf{Java}}

\begin{document}
\maketitle

\section{Professional experience}

\cventry{June-August 2013}{Speciality internship}{Development of a J2EE application using the Spring framework in a Scrum project.}{\href{www.dynamease.com}{Dynamease}}{Vernon(27120)}{
  This internship took place in a young start-up : Dynamease. This company aims to supply person-to-person services. The purpose of this internship was to create a J2EE prototype on this subject. To do so, I used the Spring framework and some of its modules (MVC, Security, Social...). I also used various social networks apis : facebook, twitter, linkedin... This project was managed using the SCRUM method.  \\
  \textbf{Key accomplishment :} participation in a new software development from scratch to release;\\
  \textbf{Language \& frameworks:} \java{} (Spring, Spring MVC, Spring Security, Spring Social, Spring LDAP)
}

\cventry{July-August 2012}{Technician internship}{Creation of a web-application testing software using \java, Selenium Driver and JUnit}{\href{www.bebook.com}{Bebook}}{Paris (75)}{
  Bebook is developping a collaborative online solution for professionals, manufacturers and their distributors. 
  Therefore, they need to be sure that their application is flawless and can support a huge number of users. During my internship, I carried out research about web testing technologies. I selected two tools relative to these problematics : JMeter and Selenium.  \\
  \textbf{Key accomplishments:} testing application using Selenium IDE, \java{} et JUnit;\\
  \textbf{Language \& frameworks:} \java{} (SeleniumRC, JUnit).
}

\section{Educational background}

\subsection{Cursus}

\cventry{2011-2014}{Information Systems Architecture Department}{}{INSA Rouen (National Institute of Applied Sciences)}{Rouen (76)}{Global approach of information system development, from conception to realization.}
\cventry{2008-2011}{General sciences courses}{}{INSA Rouen}{Rouen (76)}{}

\subsection{School project}

\cventry{2013}{Certified INSA Projet (ISO 9001)}{Development of an analysis, research and data processing software}{A2iA}{INSA Rouen (76), France}{
  Certified INSA Projects are one year long projects where teams of INSA students work for an enterprise. In my case, I work for A2iA. A2iA is a worldwide leader in intelligent word and handwriting recognition. They use a huge mass of data to analyse documents. Therefore, they need a quick and centralized access to all these datas.\\ Our project is to develop an application enabling the user to gain an easy access to these datas. The application will also analyse and process the datas stored. \\
  \textbf{Language \& frameworks:} Python (Django)
}
\cventry{2013}{Datamining project}{}{}{}{Implementation of various classification methods and algorithms : \textbf{kohonen maps}, \textbf{svms}, \textbf{multilayer perceptron}...\\
  \textbf{Language :} \matlab}
\cventry{2013}{Image recognition project}{}{}{}{Development of an image recognition software using various machine learning methods (\textbf{KNN}, \textbf{CHA}, \textbf{K-means}). \\\textbf{Language :} \matlab}
\cventry{\textbf{2012}}{Network project}{}{}{}{
  Realization of a basic HTTP server from scratch using C and sockets.\\
  \textbf{Language :} C
}
\newpage{}
\subsection{Formation}
\cvline{\textbf{Technology}}{Operating System (Linux), Databases}
\cvline{\textbf{Mathématics}}{Numerical analysis, \textbf{Datamining}, \textbf{Statistics}, \textbf{Machine Learning}, Image processing}
\cvline{\textbf{IT}}{Algorithmic, UML, Network}
\cvline{\textbf{Enterprise}}{Project management, Accounting, Law}

\section{Computer skills}
\cvcomputer{\textbf{Tools}}{Eclipse, SVN, GIT}{\textbf{Modeling}}{UML : Dia}
\cvcomputer{\textbf{Languages}}{\java, Python, \matlab, C, \textbf{SQL}}{\textbf{OS}}{Linux, Emacs}

\section{Spoken languages}
\cvline{\textbf{French}}{Native language}
\cvline{\textbf{English}}{Fluent (TOEIC score : 975/990)}
\cvline{\textbf{German}}{Intermediate level}

\section{Side projects}
\cvline{\textbf{Association}}{Creation of the INSA Rouen student choir.}
\cvline{\textbf{Video games}}{Organization of video games tournaments.}

\section{Personnal interests}
\cvline{\textbf{Sport}}{Muay Thai}
\cvline{\textbf{Video games}}{Computer games}
\cvline{\textbf{Music}}{Clarinet, choir}

\end{document}